### 2016-07-30 Doc/MSelection/mselection.tex
pois

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
\chapter{M-Selection}
\section{Introduction}
Continuous evolution of bacteriophage is becomming a potent protein engineering
tool\cite{pace}\cite{monsanto}.
For example, PACE - Phage Assisted Continuous Evolution described by Esvelt,Carlson and Lui. 
%M13 genes
%I(assembly),
%II(replication init),
%X (DNA accumulation, inside gII) 
%III(fusion),
%IV(assembly),
%V(destabilizing protein),
%VI(minor coat),
%VII(minor coat),
%VIII(major coat),
%IX(minor coat),
The continuous evolution process produces a viral genome containing a gene
which has undergone many generations of mutation and selective pressure for
a particular property.  The generality of this approach to protein engineering
is only limited by our ability to create a selection mechanism for the desired
property and insert an expressable initial form of the gene into the virus.

@@

\item{}
A modified viral genome missing a gene required for infectious progeny.

\item{}
A modified host genome/plasmid to induce an elevated mutation rate.

\item{}
A modified host genome/plasmid to provide a selection mechanism to provide
the missing gene product in proportion to the desired activity of the evolving
gene.
\end{itemize}

Extremely high in vivo mutation rates are now possible\cite{mutation}.  With M-selection, these high rates will correspond to little or none of the desired activity, these lines of descent will be subject to catastrophic levels of mutation and low probabilities of faithful reproduction. The modulation of mutation rate within each host cell means that one of these wildly mutating strains could find an environment for faithful reproduction if it should stumble upon a promising mutation in the evolving gene.

which simply modulates the rate of mutation by producing a mutagenesis suppressor from the desired activity of the evolving protein.  Improvements in the desired activity will result in a higher percentage of faithful copies of the parent genome in the succeeding generation.

@@

Effectively, the number of infectious progeny is proportional to the activity
of the selection mechanism. In principle, if the current mutation of the gene
produces a product with none of the desired activity, none of the infectivity
protein will be produced by the host, and there will be no infectous progeny.
This process involves a continuous flow of host cells through a reaction vessel
and so any genotype producing less than two infectious virions per host will
be washed out.

M-Selection is proposed to the selection mechanism by combining it with
the mechanism for elevated mutation.

@@

The virus is not crippled, but only has an additional gene or domain, similar to
phage display.

@@

For example, if the selection mechanism stimulated by the desired activity will consist
of a repressor for the production of mutagenic polymerase II-.
Positive selection is the result of reduced mutation, resulting in more clones of the
selected virus relative to its mutants.

As far as we know, modulation of the mutation rate within a particular host has
not been exploited in this way.  This form of albeit un-natural selection is referred to
as M-selection, whereby the selection mechanism consists of reducing the rate of mutation
acting on a particular instance of the viral genome precisely because it is having some
desired behavior.

@@

\subsection{Difficulties of working with crippled Virus genome}

\begin{eqnarray}
\label{eq:schemeP}
	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
\end{eqnarray}

\subsection*{Multiplicity of Infection}

\vskip 0.2cm
\begin{eqnarray}
\label{eq:MOI}
\mathrm{P}\left( x \right) = \frac{{e^{ - \lambda } \lambda ^x }}{{x!}}
\end{eqnarray}

>>>>

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
Continuous evolution of bacteriophage is becomming a potent protein engineering
tool\cite{pace}\cite{monsanto}.
For example, PACE - Phage Assisted Continuous Evolution described by Esvelt,Carlson and Lui. 
%M13 genes
%I(assembly),
%II(replication init),
%X (DNA accumulation, inside gII) 
%III(fusion),
%IV(assembly),
%V(destabilizing protein),
%VI(minor coat),
%VII(minor coat),
%VIII(major coat),
%IX(minor coat),
Continuous evolution rapidly produces a viral genome containing a gene
which has undergone many generations of mutation and selection for
a particular property.  The generality of this approach to protein engineering
is limited by our ability to insert an expressable initial gene into the phage and create a selection mechanism for the desired activity.

@@

\item{}
A modified viral genome replacing a crucial phage gene with a gene to be evolved.

\item{}
A transformed host with inducible mutagenesis.

\item{}
A host plasmid containing a selection mechanism to provide the crucial phage gene in proportion to the desired activity of the evolving gene.
\end{itemize}

\section{M-Selection}
Extremely high in vivo mutation rates are now possible\cite{mutation}.  With M-selection, these high rates will correspond to little or none of the desired activity, these lines of descent will be subject to catastrophic levels of mutation and low probabilities of faithful reproduction. The modulation of mutation rate within each host cell means that one of these wildly mutating strains could find an environment for faithful reproduction if it should stumble upon a promising mutation in the evolving gene.

The percentage of phage progeny which are exact copies of the parent is given by the Poisson distribution where $$\lambda$$ is the mutation rate per virion (mutation rate/base * 6000bp/ genome). The probability of a virion with zero mutations is:
\vskip 0.2cm
\begin{eqnarray}
\label{eq:POC}
\mathrm{P}\left( 0 \right) = \frac{{e^{ - \lambda } \lambda ^0 }}{{0!}}
\end{eqnarray}

Taking a phage production average of 100/hour for normal M13 infection requires us to have a clone rate of at least 2\%: Two faithful copies per infection in order to avoid washout.  A slower flow rate would lower this minimum fraction.

M-selection may allow for, or even require a flow rate which changes over the course of the experiment.  A ramping up of the flow rate would be appropriate

PACE is designed to keep the transit time of host cells through the lagoon to be on the order of one generation.  However, at very high levels of mutation it seems unlikely that multiple generations of viable E. coli mutants can be produced.

If the desired activity of the evolving protein produces a mutagenesis repressor, improvements in the desired activity will result in a higher percentage of faithful copies of the parent genome in the succeeding generation.

@@

In PACE, the number of infectious progeny is proportional to the activity
of the selection mechanism. In principle, if the current mutation of the gene
produces a product with none of the desired activity, none of the infectivity
protein will be produced by the host, and there will be no infectous progeny.
This process involves a continuous flow of host cells through a reaction vessel
and so any genotype producing less than two infectious virions per host will
be washed out.

@@

The virus is not crippled, that is, no critical genes need to be removed from the virion, and no phage genes are required in a host plasmid.  This avoids the problem associated with the presence of gIII in the host and improves our ability to propagate phage prior to the evolution experiment.  Of course, care must be taken to ensure that the evolving gene is not discarded before the experiment begins.  However, M13 with one additional gene(domain) is exactly what has been perfected in phage display.

@@

As far as we know, modulation of the mutation rate within a particular host has
not been exploited in this way.  We refer to this as M-selection, wherein the selection mechanism consists simply of reducing the rate of mutation.

@@
